The connection between star formation rate and dark matter halo mass in the epoch of reionization

### 2015-04-24 paper/ms.tex
removing generic text on the star formation rate

\keywords{galaxies: high-redshift --- methods: numerical} 
\begin{abstract}
We present updated constraints on the relationship between the star
formation rate and dark matter halo mass at redshift $z\sim 6$.
The observational basis for our work is the luminosity function data
obtained with from CFHTLS, HST Legacy Survey and UKIDSS.
The constrains are based on an abundance matching methodology using data
from cosmological N-body simulations in order to take into account the impact
of cosmic variance in our estimates.
We also measure the influence on the results of the dust extinction
scaling derived from observations by Bouwens.
We compare our results against the results of abundance matching
methods, a semi-analytic model of galaxy formation (GALFORM) and a
hydrodynamical simulation (Illustris).
\end{abstract}

@@

\section{Observational Background}
\label{sec:theo}

\subsection{Star Formation Rate}

The age of a star can be estimated by analyzing its spectrum. But when far
galaxies are studied, individual stars can not be resolved. Is not 
possible to make a detailed census of the galaxy popullation. Only is possible 
to get information from the whole stellar population, an integrated spectrum.

There is a  method\citep{madau98} in wich a linear relation between SFR
and luminosity in specific wavelength ranges can be assumed. This model allows
to estimate the young stars fraction and the mean SFR over periods of $10^8 -
10^9 \textrm{yr}$\citep{kennicutt98}. The luminosity in the model, comes from
the UV and the FIR broadband, also from speciffic recombination lines.

In a typical galaxy spectrum the visible wavelengths are dominated by the main 
sequence stars (A to early F) and G-K giants. In few wavelength ranges we have 
a significative contribution from the young stars rather than the old stars. 
The infrared and far infrared wavelengths emission is dominated by dust, this 
dust is  heated by the whole stellar popullation, in particular by young, 
UV-bright stars \citep{law11}.

On active galaxies the UV broadband emission is dominated by late-O
and early-B type stars, with temperature near to 40.000K. These hot and massive
stars has a lifetime below $10^7\textrm{Gyr}$, they spend their nuclear fuel
faster than smaller and cooler sunlike stars.

>>>>

\keywords{galaxies: high-redshift --- methods: numerical} 
\begin{abstract}
We present updated constraints on the relationship between the star
formation rate and dark matter halo mass at redshift $z\sim 6$.
The observational basis for our work is the restframe UV luminosity
function data obtained with CFHTLS, HST Legacy Survey and UKIDSS.
The constrains are based on an abundance matching methodology using data
from cosmological N-body simulations in order to take into account the impact
of cosmic variance in our estimates.
We also measure the influence on the results of the dust extinction
scaling derived from observations by Bouwens.
We compare our results against the results of abundance matching
methods (to the stellar mass), a semi-analytic model of galaxy
formation (GALFORM) and a hydrodynamical simulation (Illustris).
\end{abstract}

@@

\section{Observational Constraints}
\label{sec:theo}
